---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# chartcatalog

<!-- badges: start -->
[![R-CMD-check](https://github.com/growthcharts/chartcatalog/workflows/R-CMD-check/badge.svg)](https://github.com/growthcharts/chartcatalog/actions)
[![R-CMD-check](https://github.com/growthcharts/chartcatalog/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/growthcharts/chartcatalog/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The `chartcatalog` package contains tools to

- Lookup available charts in JAMES;
- Create and parse chart codes;
- Find outcomes, chart group and growth reference;
- Obtain viewport number and transformation functions;
- Lookup break points from the brokenstick model.

## Installation

You can install the development version `chartcatalog` by

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("growthcharts/chartcatalog")
```

There is no release on CRAN.

## Example 1: Available charts in JAMES

```{r setup, echo=FALSE, hide=TRUE}
library(chartcatalog)
```

The current catalogs holds `r length(unique(ynames_lookup$chartcode))` Dutch charts.

```{r example}
library(chartcatalog)
head(ynames_lookup)
length(unique(ynames_lookup$chartcode))
```

The charts are subdivided into three groups: 

```{r chartgrp}
unique(ynames_lookup$chartgrp)
```

There are five outcomes, but not every outcome (`yname`) appears in all chart groups:

```{r charttable}
with(ynames_lookup, table(chartgrp, yname))
```

## Example 2: Chartcode creating and parsing

A `chartcode` identifies the type of growth chart. The code
is a combination of 4--7 alphanumeric characters. The `create_chartcode()` 
and `parse_chartcode()` functions can be used to obtain information 
from the codes. For example, 

```{r parse}
parse_chartcode(c("HJAA"))
```

shows that chart with code `"HJAA"` identifies the front of the chart for 
Hindustan boys living in the Netherlands, design A (A4 size, 0-15 months).

## Example 3: Find outcomes, chart group and growth reference

If we have a chart code, we may find its chart group and outcomes as

```{r getchartgrp}
get_chartgrp("PJEAN26")
get_ynames("PJEAN26")
```

We obtain the call to the `clopus` package to the post-natal growth reference 
of weight of preterms born at a gestational age of 26 week by

```{r getcall}
call <- get_reference_call("PJEAN26", yname = "wgt")
call
```

This call can be stored as a shortcut to the reference. Use `eval(parse(text = call))` to execute the call.
Alternatively, if you have `clopus` installed, we may obtain the reference directly by

```{r getref}
tb <- get_reference("PJEAN26", yname = "wgt")
slotNames(tb)
head(data.frame(tb@table@table))
```

More details can be found in the `info` slot:

```{r tbinfo}
tb@info
```

## Added support for `nlreferences` package

```{r}
library(centile)
library(nlreferences)
library(dplyr)
refcode <- get_refcode("PJEAN26", "wgt")
ref <- load_reference(refcode, pkg = "nlreferences", verbose = TRUE)
head(ref)
```

